---
title: "mrubiog2000_OriginalHomeworkCode_02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


QUESTION 1. What is the probability that she will hear more than 8 calls during any given session?

```{r}
L <- 15 #Lambda value: average events (titi calls) in Poisson distribution.
x <- 1:8 #9 is the minimum number of calls required in the problem.

calls1 <- ppois(q = x, lambda = L) #We calculate the cumulative probability of hearing 1 call, 2 calls, 3 calls... till 8 calls.

1 - calls1

#We calculate the probability of NOT hearing 1 nor 2, nor 3... nor 8 calls. That means the probability of hearing more than 8 calls.

```

QUESTION 2. What is the probability that she will hear no calls in a session?

```{r}

dpois(x = 0, lambda = L) #Probability of hearing no calls (x=0)


```

QUESTION 3. What is the probability that she will hear exactly 3 calls in a session?

```{r}

dpois(x = 3, lambda = L) #Probability of hearing 3 calls (x=3).

```

QUESTION 4. Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}

x <- c(0:30)

barplot(ppois(q = x, lambda = L), 
  ylim = 0:1, #Interval showed in the "Y" axis.
  space = 0,
  names.arg = x, #Used to label each bar of the plot.
  xlab = "number of calls", 
  ylab = "prob(x)", #Name of axis.
  main = "Mass function in range 0 < x < 30", #Title of the plot.
  col="light blue"
        )
#Bar Plot where it is represented the mass function in range 0 ≤ x ≤ 30.

```

QUESTION 5. Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}

rpois(n = 104, lambda = L)

#The function "rpois" generate "n" random results following the Poisson's distribution with a given value for lambda.

```

QUESTION 6. Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
sim <- rpois(n = 104, lambda = L) #Necessary to set a vector with the function to apply it to the histogram.
hist(sim, 
     plot = TRUE, #Necessary to make a plot.
     xlim = c(0, 30), #To set the limits of the "x" axis (necessary to use "c()" structure).
     xlab = "number of calls",
     ylab = "Frequency",
     main = "Histogram 104 sessions",
     col = "pink"
     )

#Histogram that shows the frequency of the results (number of calls) of 104 "hearing titis" sessions, but only from "0-30 calls" (probabilities higher than 30 are practically 0).
```

```{r}
#Problem 1: Although now it seems obvious, I struggled the most trying to understand what was my "x" values in the first problems. I thought it was the number of the possibles calls within a day, so I could not find any value. SOLUTION: I checked notes from my statistics course (that I had totally forgot) and red Module 8 explanation again so I understood better Poisson's distribution.

#Problem 2: I did not know how to obtain random values in the Poisson's distribution for question 4. SOLUTION: I searched in the "help" section the function "dpois" I had used before to see if there was an option to set random values. In that page I found the explanation for "rpois" function.

#Problem 3: I could not set the "xlim" function in the histogram from question 6, because R told me writing "0:30", as I did in the previous plot, was not correct. The syntax was not indicated in the "help" section for "histogram" either. SOLUTION: I googled it and found an example of a code.

```