---
title: "mrubiog2000_FinalHomeworkCode_03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


QUESTION 1. What is the probability that she will hear more than 8 calls during any given session?

```{r}
L <- 15 #Lambda value: average events (titi calls) in Poisson distribution.
ppois(q = 8, lambda = L, lower.tail=FALSE)

#I have used the ppois function (cumulative) and the option "lowe.tail" to calculate probabilities that are under 8 (X > 8). This was a Diego's idea.
```
*this is good, because the ppois automatically takes the lower tail (so the probability of less than 8). For this reason, you can also do 1-ppois(8, 15) -Mel*

QUESTION 2. What is the probability that she will hear no calls in a session?

```{r}
dpois(x = 0, lambda = L) #Probability of hearing no calls (x=0)
```


QUESTION 3. What is the probability that she will hear exactly 3 calls in a session?

```{r}
dpois(x = 3, lambda = L) #Probability of hearing 3 calls (x=3).
```


QUESTION 4. Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
y <- c(0:30)
barplot(dpois(x = y, lambda = L),
  ylim = 0:1/8, #Interval showed in the "Y" axis.
  space = 0,
  names.arg = y, #Used to label each bar of the plot.
  xlab = "number of calls", 
  ylab = "prob(x)", #Name of axis.
  main = "Mass function in range 0 < x < 30", #Title of the plot.
  col="light blue"
        )
#Bar Plot where it is represented the mass function in range 0 ≤ x ≤ 30. 
#I changed the "ppois" function with the "dpois" function in order to calculate the mass function instead of the cumulative function as I did before.
```


QUESTION 5. Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
rpois(n = 104, lambda = L)
#The function "rpois" generate "n" random results following the Poisson's distribution with a given value for lambda.
```


QUESTION 6. Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
sim <- rpois(n = 104, lambda = L) #Necessary to set a vector with the function to apply it to the histogram.
hist(sim,
     xlim = c(0, 30), #To set the limits of the "x" axis (necessary to use "c()" structure).
     xlab = "number of calls",
     ylab = "Frequency",
     main = "Histogram 104 sessions",
     col = "pink",
     breaks = seq(from = 1, to = 30, by = 1), #Used to divide the histogram (Diego's idea)
     probability = TRUE #To show probabilities instead of frequencies (Diego's idea)
     )
#Histogram that shows the probability of the results (number of calls) of 104 "hearing titis" sessions, but only from "0-30 calls" (probabilities higher than 30 are practically 0).
```


```{r}
#Problem 1: Although now it seems obvious, I struggled the most trying to understand what was my "x" values in the first problems. I thought it was the number of the possibles calls within a day, so I could not find any value. SOLUTION: I checked notes from my statistics course (that I had totally forgot) and red Module 8 explanation again so I understood better Poisson's distribution.

#Problem 2: I did not know how to obtain random values in the Poisson's distribution for question 4. SOLUTION: I searched in the "help" section the function "dpois" I had used before to see if there was an option to set random values. In that page I found the explanation for "rpois" function.

#Problem 3: I could not set the "xlim" function in the histogram from question 6, because R told me writing "0:30", as I did in the previous plot, was not correct. The syntax was not indicated in the "help" section for "histogram" either. SOLUTION: I googled it and found an example of a code.
```

*Great work! and thanks for including your challenges and solutions :) -Mel*